\documentclass[10pt, twocolumn, twoside, letterpaper]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage[activate={true, nocompatibility}, final, tracking=true, kerning=true, spacing=true, factor=1100, stretch=10, shrink=10]{microtype}
% \linespread{0.95}

\makeatletter
\def\mycopyrightnotice{
  {\footnotesize
  \begin{minipage}{\textwidth}
  \centering
  978-1-6654-8872-3/22/\$31.00 \copyright2022 IEEE
  \end{minipage}
  }
}
\def\ps@IEEEtitlepagestyle{
  \def\@oddfoot{\mycopyrightnotice}
  \def\@evenfoot{}
}

\ifCLASSINFOpdf
   \usepackage[pdftex]{graphicx}
\else
   \usepackage[dvips]{graphicx}
\fi

\ifCLASSOPTIONcompsoc
  \usepackage[caption=false, font=normalsize, labelfont=sf, textfont=sf]{subfig}
\else
  \usepackage[caption=false, font=footnotesize]{subfig}
\fi

\usepackage{amsmath}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{stfloats}
\usepackage{url}
\usepackage{siunitx}
\usepackage{fancyref}

\usepackage{geometry}
\geometry{letterpaper, top=0.7in, bottom=0.7in, left=0.65in, right=0.65in}

\input{glossary}

\usepackage[style=ieee, doi=false, isbn=false, url=false, maxbibnames=1, minbibnames=1, maxcitenames=1, mincitenames=1, backend=biber, defernumbers=false]{biblatex}
\addbibresource{./bibtex/bib/Biblio.bib}

% \AtEveryBibitem{\clearfield{month}}
% \AtEveryBibitem{\clearfield{day}}
% \AtEveryBibitem{\clearfield{volume}}
% \AtEveryBibitem{\clearfield{issue}}
% \AtEveryBibitem{\clearfield{pages}}
% \AtEveryBibitem{\clearfield{number}}
% \AtEveryBibitem{\clearfield{title}}
% \AtEveryBibitem{\clearfield{isbn}}
% \AtEveryBibitem{\clearfield{keywords}}
% \AtEveryBibitem{\clearfield{issn}}
% \AtEveryBibitem{\clearfield{journal}}

\begin{document}

\title{
    % \vspace{-0.75cm}

    Data Driven Surrogate Signal Extraction for Dynamic PET Using Selective PCA
}

\pagestyle{plain}
\pagenumbering{gobble}

\author{
    % \vspace{-0.2cm}

    Alexander~C.~Whitehead~\IEEEmembership{Student~Member,~IEEE},
    Kuan-Hao~Su,
    Elise~C.~Emond,
    Ander~Biguri,
    Maria~Machado,
    Joanna~C.~Porter,
    Helen~Garthwaite,
    Scott~D.~Wollenweber~\IEEEmembership{Senior~Member~IEEE},
    Jamie~R.~McClelland and
    Kris~Thielemans~\IEEEmembership{Senior~Member,~IEEE}

    \thanks{Manuscript received November 19, 2022.}
    \thanks{This research was supported by GE Healthcare, the NIHR UCLH Biomedical Research Centre and the UCL EPSRC Centre for Doctoral Training in Intelligent, Integrated Imaging in Healthcare (i4health) grant (EP/L016478/1).}
    \thanks{The software used was partly produced by the Computational Collaborative Project on Synergistic Biomedical Imaging, CCP SyneRBI, UK EPSRC grant (EP/T026693/1).}
    \thanks{Jamie~R.~McClelland is supported by a Cancer Research UK Centres Network Accelerator Award grant (A21993) to the ART-NET consortium and a CRUK Multi-disciplinary grant (CRC 521).}
    \thanks{Alexander~C.~Whitehead was with the Institute of Nuclear Medicine, University College London, London, UK and the Centre for Medical Image Computing, University College London, London, UK. He is now with the Department of Computer Science, University College London, London, UK (contact: \texttt{alexander.whitehead.18@ucl.ac.uk}).}
    \thanks{Kuan-Hao~Su and Scott~D.~Wollenweber are with Molecular Imaging and Computed Tomography Engineering, GE Healthcare, Waukesha, USA}
    \thanks{Elise~C.~Emond, was with the Institute of Nuclear Medicine, University College London, UK. She is now with Snke OS, Munich, Germany}
    \thanks{Ander~Biguri was with the Institute of Nuclear Medicine, University College London, UK. He is now with the Department of Applied Mathematics and Theoretical Physics, University of Cambridge, Cambridge, UK}
    \thanks{Maria~Machado and Kris~Thielemans are with the Institute of Nuclear Medicine, University College London, London, UK.}
    \thanks{Joanna~C.~Porter and Helen~Garthwaite are with the Centre for Respiratory Medicine, University College London, London, UK.}
    \thanks{Jamie~R.~McClelland and Kris~Thielemans are with the Centre for Medical Image Computing, University College London, London, UK}
}

\maketitle
\IEEEpeerreviewmaketitle

\begin{abstract}
    Respiratory motion correction is beneficial in PET. Methods of motion correction include gated reconstruction, where the acquisition is binned, based on a respiratory trace. To acquire these respiratory traces, an external device, like the Real Time Position Management System, or a data driven method, such as PCA, can be used. Data driven methods have the advantage that they are non-invasive, and can be performed post-acquisition. However, data driven methods have the disadvantage that they are adversely affected by the tracer kinetics of a dynamic acquisition. This work seeks to evaluate several adaptions of the PCA method, through which it can be used with dynamic data. The methods explored in this work include, using a moving window (similar to the KRG method of Schleyer et al. (PMB 2014)), extrapolation of the principal component from later time points to earlier time points, as well as a method to select and combine multiple respiratory components. The respiratory traces acquired, were evaluated on $21$ patients, by calculating their correlation with a Real Time Position Management System surrogate signal. The results indicate that all methods produce better surrogate signals than when applying static PCA to dynamic data. Extrapolating a late principal component, produced more promising results than using a moving window, and selecting and combining components held benefits for all methods.
\end{abstract}

% \vspace{-0.5cm}

\input{body}

% \vspace{-0.5cm}

% \AtNextBibliography{
    % \scriptsize
%     \small
% }
\printbibliography

\end{document}
